### 2017-05-10 paper/response.Rmd

# Response to reviewers

I would like to thank the reviewers for taking the time to review visdat so thoroughly. It is fantastic to hear such encouraging comments from members of the community.

I will now respond to suggested changes and other constructive criticisms.

@@

# @seaaan's Review

1. Documentation: README

> The README is very good! It gives a helpful overview of everything in the package and is clearly written, with good examples. All of the code examples worked on my computer. You might consider breaking the "experimental" parts of the package into a separate README like you do with the vignettes.

- Agreed, but I would prefer to keep the README as a whole piece, so I think instead I will just link to the experimental vignette as in the README. This has been logged in [issue 39](https://github.com/njtierney/visdat/issues/39) and fixed in the indicated commit messages.

@@

> Link to the vignettes from the README.

- Agreed, this has been addressed in [issue 39](https://github.com/njtierney/visdat/issues/39)

@@

> The title of the github project is "A package to assist in visually testing a dataset", which doesn't describe the project that well. I suggest changing it to be the same title as on the DESCRIPTION file, which is effective in quickly summarizing what the package does.

- Agreed, this makes more sense - changed!

> You don't introduce the airquality data set at first usage, but you do introduce it after the second plot. Move the introduction to first use.

- Thank you for this, this has been addressed in [issue 39](https://github.com/njtierney/visdat/issues/39).

@@

> I don't understand this sentence: "When there is <0.1% of missingness, vis_miss indicates that there is >1% missingness."

- Agreed, this has been changed in [issue 39](https://github.com/njtierney/visdat/issues/39).

@@

> I don't know why, but in the plotly section, a vis_dat() (non-interactive) plot of df_test appears between the first two interactive plots. I can't explain it, hopefully it's just a weird quirk on my computer.

- I can't seem to replicate this, can you maybe take a screenshot of this?

> There is a "future work and experimental features" section in the "Using visdat" vignette -- I suggest transferring that to the experimental vignette and just linking to it from the "Using visdat" vignette. Perhaps move the vis_guess() and the interactive plots to the experimental features vignette as well, since they seem to be evolving.

- Agreed, I have now linked to this additional experimental vignette in the "using visdat" vignette.

@@

# Function documentation

> Did you mean to export guess_type()?

- Yes, as I thought that it might be a useful function for users, although I can't think of a good usecase outside of `vis_guess` right now. Perhaps it might be best for `guess_type` to be unexported?

> Formatting: links, code, and other formatting need to be done with .Rd syntax. For example, for code, use \code{}, not backticks. For bold, use \strong{} instead of asterisks.

- I have now converted this over to use markdown with roxygen.

@@

> Return values: The documentation doesn't include the "Value" section which is typically used to say what a function returns. I would add this. E.g. @return A \code{ggplot} object displaying the type of values in the data frame and the position of any missing values.

- Thank you for this - this has been changed for `vis_dat.R`, `vis_compare.R`, `vis_guess.R`, and `vis_miss.R`.

@@

> ?vis_miss_ly: The reference to vis_miss in the "See Also" section should be a link. Like this: \code{\link[visdat]{vis_miss}}

- Thank you for this comment, this has been updated.

> ?visdat: It's good that this page exists. However, it doesn't have any content -- add a brief overview of the package with links to the documentation page for the main functions.

- Excellent point, I have addressed this in this [commit](https://github.com/njtierney/visdat/commit/106e24a4e186519f6ede615c3b2822073a03d780)

@@

# Examples

> Don't need to call library for either visdat or packages you use internally (only if you actually call a function from another package in the example code itself).

- Great point, thanks for picking up on this, I have made the final changes [here](https://github.com/njtierney/visdat/commit/d71d2ac8c0708a327d51217f0298b4d3dec2b970)

- thank for you picking up on this, this was fixed [here](https://github.com/njtierney/visdat/commit/31909e241c1e1cc1b640c55edaea9c228f92976e)

@@

> example(vis_guess): gives warning message

# Community guidelines

> There are no guidelines for how to contribute, either in the README or in a CONTRIBUTING file.

- This has now been added [here](https://github.com/njtierney/visdat/commit/c7ea5bb6bb12a43719fc4dbdfbccc22153072b62).

@@

# JOSS

> The paper seems more detailed than most other JOSS papers and goes into specific functions. Additionally, does JOSS allow figures? I didn't see any in the papers I looked at or see mentions of them in the author guidelines. But I'm not an expert on JOSS, so maybe someone else can weigh in on that.

- I believe JOSS allows figures - the tidytext paper [has a figure](http://joss.theoj.org/papers/89fd1099620268fe0342ffdcdf66776f).

@@

> The paper doesn't have any references in the "References" section, but does have inline references.

- These references are provided in the yaml, and in a .bib file - hopefully these get compiled with the JOSS paper, but perhaps @arfon can chime in here.

@@

> If you keep it, make sure you have permission to reproduce the image from R4DS.

- I have removed the figure now, in favour of your suggestion to keep things simpler.

@@

# Functionality

## Common issues

> It is unintuitive to me to have the rows in reverse order (i.e. row 1 at the bottom) and for the columns to be clustered by type, rather than appear in the order they appear in the data frame. I think the default behavior should be for rows and columns to appear in the same order as in the input. Additionally, always putting the titles at the top of the columns makes sense to me. Including sort_type as an option might be useful, but by default it should be off. I'm not quite sure of the use case for the flip argument, but maybe there is one!

- I agree that the rows should be in the order that you see the dataframes. I would also prefer for the

- The flip argument was placed there to experiment with this idea of flipping the

### 2017-05-12 paper/response.Rmd

# Response to reviewers

I would like to thank the reviewers for taking the time to review visdat so thoroughly. It is fantastic to hear such encouraging comments from members of the community.

Below I respond to suggested changes and other constructive criticisms.

@@

# @seaaan's Review

1. Documentation: README

> You might consider breaking the "experimental" parts of the package into a separate README like you do with the vignettes.

- Agreed! I would prefer to keep the README as a whole piece, Perhaps instead I could just link to the experimental vignette as in the README. This has been logged in [issue 39](https://github.com/njtierney/visdat/issues/39) and fixed in the indicated commit messages.

@@

- Agreed, this has been changed in [issue 39](https://github.com/njtierney/visdat/issues/39).

2. Vignettes:

> Make sure you have permission to reproduce the image from R4DS. The first few paragraphs of the "Using visdat" vignette are a bit unnecessary in my opinion. You could start much more simply, with something like: "When you get a new data set, you need to get a sense of what it contains and potential problems with it." and then continue with the discussion of different ways to approach this challenge (e.g. head, glimpse, ...).

- I agree with you that this is a clearer way to introduce the topic - this is now [changed](https://github.com/njtierney/visdat/commit/3f74141d2e9de4bc0ae870fc874b17a21829618e).

@@

> In the "Using visdat" vignette, it says "missing data represented by black", but it shows up as gray on my computer.

- I think I've fixed this now, does it still happen?

> I don't know why, but in the plotly section, a vis_dat() (non-interactive) plot of df_test appears between the first two interactive plots. I can't explain it, hopefully it's just a weird quirk on my computer.

- I can't seem to replicate this, can you maybe take a screenshot of this if this is still happening?

@@

> There is a "future work and experimental features" section in the "Using visdat" vignette -- I suggest transferring that to the experimental vignette and just linking to it from the "Using visdat" vignette. Perhaps move the vis_guess() and the interactive plots to the experimental features vignette as well, since they seem to be evolving.

- Great point! Thank you! I have now linked to this additional experimental vignette in the "using visdat" vignette.

@@

> Did you mean to export guess_type()?

- Yes, as I thought that it might be a useful function for users, although I can't think of a good usecase outside of `vis_guess` right now. Perhaps it might be best for `guess_type` to be unexported?

> Formatting: links, code, and other formatting need to be done with .Rd syntax. For example, for code, use \code{}, not backticks. For bold, use \strong{} instead of asterisks.

- I have now converted this over to use markdown with roxygen, this should be fixed now.

@@

> Return values: The documentation doesn't include the "Value" section which is typically used to say what a function returns. I would add this. E.g. @return A \code{ggplot} object displaying the type of values in the data frame and the position of any missing values.

- Thank you for this - this has been changed for `vis_dat.R`, `vis_compare.R`, `vis_guess.R`, and `vis_miss.R`.

> ?vis_compare: The documentation for this function needs to be updated. It is more a list of ideas for how to implement the function than a description of what it does.

- Thank you for this comment, this has [been updated.](https://github.com/njtierney/visdat/blob/master/R/vis_compare.R)

@@

> ?vis_guess: First sentence of description seems to have an extra word or phrase, not sure exactly what was intended.

- Thank you for this comment, this has [been updated.](https://github.com/njtierney/visdat/blob/master/R/vis_guess.R)

@@

> ?vis_miss_ly: The reference to vis_miss in the "See Also" section should be a link. Like this: \code{\link[visdat]{vis_miss}}

- Thank you for this comment, this has [been updated.](https://github.com/njtierney/visdat/blob/master/R/vis_miss_ly.R)

@@

> Don't need to call library for either visdat or packages you use internally (only if you actually call a function from another package in the example code itself).

- Great point, thanks for picking up on this, I have made the final changes [here](https://github.com/njtierney/visdat/commit/d71d2ac8c0708a327d51217f0298b4d3dec2b970)

> example(vis_dat): "palette" is misspelled.

- Thank for you picking up on this, this was fixed [here](https://github.com/njtierney/visdat/commit/31909e241c1e1cc1b640c55edaea9c228f92976e)

@@

> example(vis_compare) is a good example but gives a bunch of warning messages.

> example(vis_guess): gives warning message

- These now gives the message:

```
vis_compare / (vis_guess) is in BETA! If you have suggestions or errors
post an issue at https://github.com/njtierney/visdat/issues
```
Do you think this is OK?

@@

> The paper doesn't have any references in the "References" section, but does have inline references.

- These references are provided in the yaml, and in a .bib file - hopefully these get compiled with the JOSS paper, but perhaps @arfon can chime in here.

> If you keep it, make sure you have permission to reproduce the image from R4DS.

- I have removed the figure now, in favour of your earlier suggestion to keep things simpler - thank you for this suggestion!

@@

## Common issues

> It is unintuitive to me to have the rows in reverse order (i.e. row 1 at the bottom) and for the columns to be clustered by type, rather than appear in the order they appear in the data frame. I think the default behavior should be for rows and columns to appear in the same order as in the input. Additionally, always putting the titles at the top of the columns makes sense to me. Including sort_type as an option might be useful, but by default it should be off. I'm not quite sure of the use case for the flip argument, but maybe there is one!

> The flip argument should be available for all of the functions if you provide it for any, for the sake of consistency. Possibly also the palette argument.

- I agree that the rows should be in the order that you see the dataframes. I would also prefer for the column names to be on top of the visualisation, but I cannot seem to get the column names to present nicely here.

- The flip argument was placed there to experiment with this idea of flipping the plot - as you suggested, to have row 1 at the top. Personally, I think that now the flip argument should be removed, as I cannot now really think of any times where I would prefer the old arrangement of rows.

- I agree with you re the palette, although I'm not sure how this could work for vis_miss. But perhaps I should allow for users to insert their own pallete for this.

@@

```

> Using a helper function for this next one in particular would allow you to suppress the warning messages just once:

```
  d$value <- tidyr::gather_(x, "variables", "value", names(x))$value
```

- Thank you very much for this, I have created a helper function as you suggested, and suppressed the message in that way.

@@

> The code for flipping the rows is also duplicated:

```
 if (flip == TRUE){
    suppressMessages({
      vis_dat_plot +
        ggplot2::scale_y_reverse() +
        ggplot2::scale_x_discrete(position = "top",
                                  limits = type_order_index) +
        ggplot2::theme(axis.text.x = ggplot2::element_text(hjust = 0.5)) +
        ggplot2::labs(x = "")
    })
  } else if (flip == FALSE){
    vis_dat_plot
  }

```

- Thank you for this, I have created a helper function for these code duplications, it makes things much easier to handle! These are now in the [internals file](https://github.com/njtierney/visdat/blob/fix-functionality/R/internals.R)

@@

> vis_compare and vis_guess are indicated as being in beta, which seems also to apply to the plotly versions of the functions. The message that they emit is a helpful indication that they may change in the future. Before submitting to CRAN, however, you might consider moving those functions to the development version of the package and only uploading the functions with a stable API, then adding the beta version later once they stabilize. This is a judgment call; I think I tend towards being conservative on this issue personally.

- Agreed, I need to create a dev branch, where these experimental features can reside.

@@

> This is a minor issue, but was so thoroughly drummed into me by CS professors that I have to mention it. In calls like if (sort_type == TRUE), the == TRUE is redundant, so it's equivalent to just write if (sort_type). Similarly, if (x == FALSE) is equivalent to if (!x). There are a number of these in the code for various functions.

- I've actually not heard this before, but I can certainly understand why you would want to avoid called such as if(x == TRUE) over if(x). Personally, however, I think I actually prefer to be really explicit.

@@

> Inside of the first if-block, there are some comments about arranging columns in order of missingness, but as far as I can tell, that is not done.

## vis_miss()

> It would be cool to indicate the % missing for each column individually (maybe in column labels?) like how you indicate the % missing for the data overall.

- great suggestion, this has been added! And can be turned off in the options with `show_perc_col == FALSE`

@@

## vis_compare()

> This is a neat function! It would be cool if you could generalize it to also handle data frames of unequal dimensions, perhaps by showing which rows/columns are only in one data frame or the other. Just an idea I had though, not a requirement at all!

- I am glad you like this! It is a difficult problem that I cannot work outk, re the rows/cols matching when they are out of the dimension. I'm not quite sure what to do here.

@@

## vis_miss_ly

> The pop-up window is great! Can you make it the same as for ggplotly(vis_dat())? It's especially helpful to show the row number.

> Why not have the same arguments for this function as for vis_miss?

- I will see what I can whip up in plotly, I do not know much about it at the moment, but @carson has a free book, so I'll get onto that.

@@

## vis_dat_ly()

> With vis_dat(airquality) %>% ggplotly(), the window that appears on mouseover should say "type" instead of "valueType", "variable" instead of "variables" and "row" instead of "rows"

- OK, I'm pretty sure that this is an easy fix, I just specify these things in the arguments of ggplot, which plotly reads in. The problem is then that I need to change the names of things inside of ggplot

@@

> If you provide vis_miss_ly, it makes sense to me to also provide vis_dat_ly, and possibly also vis_compare_ly and vis_guess_ly. An initial implementation could just be vis_dat(x) %>% ggplotly(), but then you have the API in place at least.

- I would prefer to build it in straight plotly, as plotly is really fast, and the process of converting ggplot plots into plotly is actually quite computationally intense

@@

- Yes, thank you for picking up on this!

# @batpigandme's review

> vis_dat's power lies in the fact that it's essentially a visual analogue to one's data, if imagined as a frame/spreadsheet. In order to enhance this, I would suggest that the charts, by default, "read" in the spirit of this analogy by going from top to bottom.

- Absolutely agree, I have made these changes now and it makes a LOT more sense to do it this way!

@@

> Added canonical link to the mi package, since you do so for wakefield

- Thank you!

> Though the README suggests that when less than one percent is missing, "vis_miss indicates that there is >1%", the chart that results from vis_miss(test_miss_df) reads Missing (<0.1%) in the legend

- Agreed, this has now been fixed, you can see this in the [README]()

> When running the first example from README, (vis_dat(airquality)), the user will get a warning re. deprecation of dmap(). If this is not of consequence to the package's functionality, then you might consider adding it to the suppressed messages. If it's something most users supress locally, then you might suggest that somewhere in the README.

@@

- This could be due to the yaml info, I have tried to run this and found ...

## Functionality

### Installation and Tests

> Installation built successfully (on three different computers, and versions of R at that), as did automated testing. Good work!

@@

- Hooray!

### Functionality

> All of the functions run as expected, and as described. My feedback here primarily concerns messages and warnings, that apply to several functions.

> Warning messages can be scary, so it's always a relief see them acknowledged or shown in vignette and/or README examples (as is done re. non-identical attributes). vis_compare (a function for which I can imagine plenty of use cases) is currently returning enough text that it may leave the user confused as to what's most important, or an error on their end, etc. Currently, running vis_compare(iris_diff, iris) (as in the given example), returns:

@@

> vis_guess is where the cell-to-row visual disparity becomes most confusing. I think this is a fantastic function, especially for beginners, and so the ability to essentially "read" the visual, as one would a table (top to bottom), would be invaluable.

- Agreed, this has been addressed by making the "flip" argument become the hard set default. I cannot honestly see

> vis_dat with plotly / interactive functions are great, and, again, here it would be even more helpful if one could "read" the charts as one would a table.

# njtierney summary response and remaining tasks to complete

This has been a fantastic process to be a part of. To summarise, the main changes that I made were:

- re-orienting the vis_* family to read in the way that one reads a dataframe
- removing many of the error messages that occur due to some tidy/dplyr collation of factors
-

Still remaining to do is:

- complete vis_guess() for release
    - Adding the fast Rcpp code for guess_type
    - remove message regarding BETA
- create `vis_dat_ly`, `vis_miss_ly`, and `vis_guess_ly` functions
- Ensure that all of the `vis_*` family functions have the same internal arguments where appropriate:
  - E.g., vis_dat, doesn't need to same clustering missingness options (or...does it?)
- move vis_compare into a "dev" branch on github
- should I export vis_guess? - Yes, as I thought that it might be a useful function for users, although I can't think of a good usecase outside of `vis_guess` right now. Perhaps it might be best for `guess_type` to be unexported?

> example(vis_guess) / example(vis_compare) : gives warning message

- These now gives the message:

```
vis_compare / (vis_guess) is in BETA! If you have suggestions or errors
post an issue at https://github.com/njtierney/visdat/issues
```
Do you think this is OK?

### 2017-06-17 paper/response.Rmd

> The paper seems more detailed than most other JOSS papers and goes into specific functions. Additionally, does JOSS allow figures? I didn't see any in the papers I looked at or see mentions of them in the author guidelines. But I'm not an expert on JOSS, so maybe someone else can weigh in on that.

- I believe JOSS allows figures - the tidytext paper [has a figure](http://joss.theoj.org/papers/89fd1099620268fe0342ffdcdf66776f).

> The paper doesn't have any references in the "References" section, but does have inline references.

- These references are provided in the yaml, and in a .bib file - hopefully these get compiled with the JOSS paper perhaps @arfon can chime in here?

@@

## Common issues

> It is unintuitive to me to have the rows in reverse order (i.e. row 1 at the bottom) and for the columns to be clustered by type, rather than appear in the order they appear in the data frame. I think the default behavior should be for rows and columns to appear in the same order as in the input. Additionally, always putting the titles at the top of the columns makes sense to me. Including sort_type as an option might be useful, but by default it should be off. I'm not quite sure of the use case for the flip argument, but maybe there is one!

> The flip argument should be available for all of the functions if you provide it for any, for the sake of consistency. Possibly also the palette argument.

- I agree that the rows should be in the order that you see the dataframes. I would also prefer for the column names to be on top of the visualisation - I have now implemented this, although I think that the presentation of the column names is perhaps not ahs nice.

- The flip argument was placed there to experiment with this idea of flipping the plot - as you suggested, to have row 1 at the top. The flip argument has now been removed, as I cannot now really think of any times where I would prefer the old arrangement of rows.

- I think that the default sort_type option should be to put all of the similar columns together - to me this makes it easier to identify what is similar, and what is different; when I start looking at a dataset I usually want to know what variables are what class. I am willing to change this, but would be interested to see what others think.

- I agree with you re the palette argument being provided for all plots, although I'm not sure how this could work for vis_miss. But perhaps I should allow for users to insert their own pallete for this. Personally I think that there should be a standard palette where the common classes (character, factor, integer, numeric, datetime, etc) each have their own distinct colour, and other classes are given different factors.

@@

```

> Using a helper function for this next one in particular would allow you to suppress the warning messages just once:

```
  d$value <- tidyr::gather_(x, "variables", "value", names(x))$value
```

- Thank you very much for this, this has bothered me for a while! I have created a helper function as you suggested, and suppressed the message in that way.

### 2017-07-02 paper/response.Rmd

- Thank for you picking up on this, this was fixed [here](https://github.com/njtierney/visdat/commit/31909e241c1e1cc1b640c55edaea9c228f92976e)

> example(vis_compare) is a good example but gives a bunch of warning messages.
> example(vis_guess): gives warning message

- These now both give warning messages like:

```
vis_compare / (vis_guess) is in BETA! If you have suggestions or errors
post an issue at https://github.com/njtierney/visdat/issues
```

Do you think this is OK?

@@

> vis_compare and vis_guess are indicated as being in beta, which seems also to apply to the plotly versions of the functions. The message that they emit is a helpful indication that they may change in the future. Before submitting to CRAN, however, you might consider moving those functions to the development version of the package and only uploading the functions with a stable API, then adding the beta version later once they stabilize. This is a judgment call; I think I tend towards being conservative on this issue personally.

- Agreed, I need to create a dev branch, where these experimental features can reside.

> This is a minor issue, but was so thoroughly drummed into me by CS professors that I have to mention it. In calls like if (sort_type == TRUE), the == TRUE is redundant, so it's equivalent to just write if (sort_type). Similarly, if (x == FALSE) is equivalent to if (!x). There are a number of these in the code for various functions.

<!-- - I've actually not heard this before, but I can certainly understand why you would want to avoid called such as if(x == TRUE) over if(x). This has now been changed. -->

@@

# vis_dat()

> Maximum data frame size: the heatmaps stop working on my computer with very large data sets. E.g. library(nycflights13); vis_dat(flights) hangs for a minute or so and then displays an empty grid. It works with 10000 rows, but not 100000. Similar issue with many columns. Especially because this package is designed for people to get a sense of new data sets, where users may not have realized how big the data are, I think it makes sense to prevent this issue. Possibilities: (1) max_rows = 10000 parameter, which stops if nrow(data) > max_rows and gives a descriptive error message. Then the user can increase the maximum or subset their data frame. Might also need to consider max_cols because 10000 rows and 2 cols is very different from 10000 rows and 500 cols. (2) Downsample the non-missing rows somehow and indicate to the user where omissions were made. (3) ???

- This is an interesting one! It was brought to my attention [here](https://github.com/njtierney/visdat/issues/32), by @MilesMcBain, but I couldn't replicate this issue. Similarly, I can actually display the nycflights data. So it seems that this is to do with the fact that computations power has a bit to do with it. I think that option 1 is the best case here, but option 2 actually gets a little bit difficult, because this leads to another issue of effectively downsampling a dataset whilst maintaining data structure. This could be a problem, say, if I did perform down-sampling and then the user looked at the data with visdat and plotly, they might get a mis-represented sample. Likewise, if there is a very large proportion of missing data, this might be difficult to preserve exactly. Ways around this might include some very explicit warning messages, or perhaps even a note directly on the plot that the data have been downsampled.

@@

> The palette argument doesn't cause color changes, as far as I can tell. I think you need to do vis_dat_plot <- vis_dat_plot + <palette>, whereas currently the value of vis_dat_plot isn't being updated in the blocks related to color palettes. Additionally, you could do ggplot2::scale_color_brewer(type = "qual", palette = "Set1") rather than explicitly writing out the color names, although the colors would be in a slightly different order than you have now.

-

> If the user provides a palette name, you should check that it's valid. If not, throw an error with a message. Currently, if you misspell a palette name, it just goes ahead with the default palette.

- Great point! I have fixed this now with:

```r

     } else  {
       warning("palette arguments need to be either 'qual' 'cb_safe' or 'default'")
     } # close else brace

at the end of `vis_dat.R`

@@

# Minor comments

> There are some lines of commented-out code: # x = airquality and # mutate_each_(funs(fingerprint), tbl_vars(.)) %>%

> Inside of the first if-block, there are some comments about arranging columns in order of missingness, but as far as I can tell, that is not done.

- Thank you for picking up on these comments, they are now removed!

@@

## vis_miss()

> It would be cool to indicate the % missing for each column individually (maybe in column labels?) like how you indicate the % missing for the data overall.

- great suggestion, this has been added! And can be turned off in the options with `show_perc_col == FALSE`.

@@

## vis_compare()

> This is a neat function! It would be cool if you could generalize it to also handle data frames of unequal dimensions, perhaps by showing which rows/columns are only in one data frame or the other. Just an idea I had though, not a requirement at all!

- I am glad you like this! It is a difficult problem that I cannot work out, re the rows/cols matching when they are out of the dimension. I'm not quite sure what to do here to make this possible, I think that this should be tackled in a future release of `visdat`.

@@

> Warning message: "1: In if (dim(df1) != dim(df2)) { : the condition has length > 1 and only the first element will be used". This is a consequence of calling dim(df1) != dim(df2). The dim function returns a two element vector in this case, but the != only compares the first element of each vector. (I.e. it's only comparing the number of rows). Instead, use !identical(dim(df1), dim(df2)).

> In the error message about data frames of unequal dimensions, you mean to say "vis_compare only handles dataframes of identical dimensions", not "does not handle".

```r

  if (!identical(dim(df1), dim(df2))){
    stop("Dimensions of df1 and df2 are not the same. vis_compare currently only handles dataframes of identical dimensions.")
  }

- Thank you for both of these comments! These have been changed in `vis_compare.R`.

@@

- Thank you for both of these comments! These have been changed in `vis_compare.R`.

## vis_guess

> vis_guess lacks some of the parameters that vis_dat has, but should have the same options (except maybe not sort_type?)

- Agree, this is a good idea, I have added a helper palette function now so that `vis_guess` and `vis_dat` can share the same palette

@@

> Then put this in readr/R/collectors.R:

```
#' @rdname parse_guess
#' @export
guess_parser_vector <- function(x, locale = default_locale()) {
  stopifnot(is.locale(locale))
  collectorGuessVector(x, locale)
}
```

> Then rebuild readr. Back in visdat, call guess_parser_vector once with the whole vector of unknowns instead of calling guess_parser repeatedly.

- OK, so I think that this is a fantastic idea! But I'm not sure on the best way to move this into production of `visdat`, since it sounds like we would need to borrow a chunk of code from readr and then modify it. I wonder if perhaps the solution here is to do a pull request for this specific feature in `readr`?

@@

> The vis_guess description is a bit hard to follow. I'd start by stating what it does do, before making the comparison to vis_dat, just so it's a bit more self-contained.

- done, great suggestion!

> The visdat and visdat-package sections are empty, when, I assume, you'll want the description to be included (right now description just says "visdat").

- Thank you for picking up on this, I've updated the main descriotion file now

@@

```
  #>  Warning messages:
  #> 1: In if (dim(df1) != dim(df2)) { :
  #>  the condition has length > 1 and only the first element will be used
  #> 2: attributes are not identical across measure variables; they will be dropped
  #> 3: attributes are not identical across measure variables; they will be dropped

```

- Agreed, this error message for vis_compare has been addressed in commit ...

> vis_compare example also seems to cluster by default (all different data is shown at the bottom, of the two columns)

@@

-

## Community guidelines

> I don't believe these are currently in the package.

- Thank you for picking up on this, I've added them now, :)

@@

> The function runs fine, and appears to have worked, but it's enough "warning" text, that it may warrant concern for the user.

- Absolutely agreed, this is a problem and barrier,

> vis_guess is where the cell-to-row visual disparity becomes most confusing. I think this is a fantastic function, especially for beginners, and so the ability to essentially "read" the visual, as one would a table (top to bottom), would be invaluable.

- Agreed, this has been addressed by making the "flip" argument become the hard set default. I cannot honestly see a good reason to use the old print method, so I have removed it to make it read top down first.

@@

> vis_dat with plotly / interactive functions are great, and, again, here it would be even more helpful if one could "read" the charts as one would a table.

# njtierney summary response and remaining tasks to complete

This has been a fantastic process to be a part of. To summarise, the main changes that I made were:

- re-orienting the vis_* family to read in the way that one reads a dataframe
- removing many of the error messages that occur due to some tidy/dplyr collation of factors
- refactoring repeated code into internal functions to more clearly express what

@@

Still remaining to do is:

- complete vis_guess() for release
    - Adding the fast Rcpp code for guess_type
    - remove message regarding BETA
- Add interactivity
  - create `vis_dat_ly`, `vis_miss_ly`, and `vis_guess_ly` functions
- Ensure that all of the `vis_*` family functions have the same internal arguments where appropriate:
  - E.g., vis_dat, doesn't need to same clustering missingness options (or...does it?)
- move vis_compare into a "dev" branch on github
- should I export vis_guess? - Yes, as I thought that it might be a useful function for users, although I can't think of a good usecase outside of `vis_guess` right now. Perhaps it might be best for `guess_type` to be unexported?

- For the moment I have decided to put visdat onto CRAN, with the main functions
being: 
  - vis_dat
  - vis_miss
  - vis_guess
- Then, in a subsequent release, I will add the interactive functions:
  - vis_dat_ly
  - vis_miss_ly
  - vis_guess_ly
  - vis_compare
- And also look into speed improvements for `vis_guess`

### 2017-07-03 README.Rmd

```{r, echo = FALSE}

@@

```{r eval = FALSE}
# install.packages("devtools")

@@

There are also experimental which are described in more detail in the vignette ["Experimental Features of visdat](http://www.njtierney.com/visdat/articles/experimental_features.html).

>>>>

```{r setup, echo = FALSE}

@@

```{r installation, eval = FALSE}
# install.packages("devtools")

@@

There are also experimental functions, which include guessing values,  comparing two dataframes, and adding interactivity. These are described in detail in the vignette ["Experimental Features of visdat](http://www.njtierney.com/visdat/articles/experimental_features.html).
